---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# team brands

# tanger_styles
r package to help with viz at tanger


For the team >> Enterprise Insights and Analytics


Font >> https://fonts.googleapis.com/css?family=Montserrat:300,400,700,900|Roboto:300,400,500,900

ticker >> SKT

Colors ...
  #000000 >> black,
  #464646 >> dark grey,
  #C00000 >> red
  
  
The goal of team_brand is to apply the brand style and identity guidelines.
This includes standards for ggplot, highcharter, datatable, kable, and reactable.
This also includes standard CSS documents for use with R Markdown generated webpages.

## Installation

```r
remotes::install_github("phildwalker/team_brand")
```

## ggplot2

```{r}
library(ggplot2)
library(team_brand)

ggplot(mtcars, aes(mpg, disp))+
  geom_point()+
  labs(
    title = "A Nice ggplot2 Graph"
  )
```


